---
title: "Developping inside shinyDiver"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shinyDiveR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: "Maxime Jaunatre"
date: "29/01/2021"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This shiny application has been build following the `{golem}` package instructions, on a framework written by ThinkR.

More ressources on the framework is present in the [package](https://rtask.thinkr.fr/fr/demarrer-avec-golem/) documentation and the [book](https://engineering-shiny.org/) written to explain the framework.

# Installation and usage

You can launch locally the application by running the following code.

```{r run, eval = FALSE}
library(shinyDiveR)
shinyDiver::run_app()
```

# Contributing guides

Please follow this guide before a pull-request on github. This is also a reminder of good practice for the application longevity and debugging.

## Adding run_app options

You can add options to the shiny application. These options allow to set parameters for the application during all it's production.

At this time, 2 options has been set :
- `app_lang`, which can be set between 'en' and 'fr'. It allow a translation of the application. 
- `app_maxd`, a numeric input allowing to define a maximum depth for all the app. It is used to restrict deeper depths for beginner student who do not need to study dive planification lower than their grades.

This options are set in the **R/run_app.R** file. You need to write them inside the function parameters, document them and add them to the **golem_opts** list. Don't forget to name the list element, this is the name to call them later on.

Parameters can be called in the ui and server functions by calling the following code :

```{r call opt, eval=FALSE}
x <- golem::get_golem_options("x")
```

## Adding supported languages

You can add a supported language by filling the **inst/app/www/translation.json** file. Note that a full language support must be done before implementing the language inside the UI, because missing sentences will be in another language by default (english or french, depending on the production server). 

Once the translation has been completed, you can run the **dev/run_dev_update_trans.R** script and check for your translation by calling this code :

```{r call opt, eval=FALSE}
shinyDiver::run_app('fr') # french language example.
```

For more information about the language support, please check [shiny.i18n package](https://github.com/Appsilon/shiny.i18n). 
